Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-01-26 2_SSL_EES/article/article_main.tex
added content to main publication

The historical improvements in four sub-efficiency channels—forward voltage efficiency, internal quantum efficiency, droop, and light extraction efficiency—identified in our study are shown in Figure 4. Using data on these four sub-efficiencies, as well as on improvements in spectral efficiency and light conversion efficiencies calculated from spectral data for LED phosphors provided in SI section 2 and discussed in the context of consumer experience improvements in section 5.2, we then calculate the overall LED efficiency in 2003 and 2010, shown in Figure XX. as a waterfall diagram across all sub-efficiencies, and in 2016 and 2020, similarly shown in Figure . The overall white LED lamp efficiency improved from $\eta_L(2003)=5.8\% \rightarrow \eta_L (2010) = 12.6\% \rightarrow \eta_L = 32.5\% \rightarrow \eta_L(2020) = 38.7\%$, as shown in Figure \ref{fgr:waterfall}. No single loss channel dominates in terms of its contribution to the overall efficiency, in line with previous observations\cite{tsao2010solid}. We note, however, that the loss channels with a fixed physical limit, e.g., the Stokes loss that contributes to the conversion efficiency by phosphors, became more dominant in 2016 and 2020 compared to 2003 and 2010.

Figure \ref{fgr:breakthroughs_efficiency} shows the overall magnitude of contributions of identified LED innovations and technology spillovers to improvements in LED efficiency over time across different sub-efficiencies. The list of technology spillovers identified in our study is provided and discussed below in Section \ref{subsec:spillovers}. Through the index decomposition analysis described in section \ref{subsec:metrics}, we find that in the overall LED efficiency increase of 32.9\% from 5.8\% to 38.7\% between 2003 and 2020, at least 2.8 of these percentage points can be attributed specifically to technology spillovers identified in this study, corresponding to 8.5\% of the total LED efficiency improvements between 2003 and 2020.

In Figure \ref{fgr:breakthroughs_efficiency} we also compare, for the first time, efficiency improvements across sub-efficiencies over time, contrasting them with the physical limits of corresponding loss channels. Notably, sub-efficiencies for the most recent devices considered in our study are only $\sim10\%$ below the physical limit. The exception is spectral efficiency, which at $\sim20\%$ below the physical limit shows larger potential for further improvements.

>>>>

The historical improvements in four sub-efficiency channels—forward voltage efficiency, internal quantum efficiency, droop, and light extraction efficiency—identified in our study are shown in Figure \ref{fgr:subeff}. Using data on these four sub-efficiencies, as well as on improvements in spectral efficiency and light conversion efficiencies calculated from spectral data for LED phosphors provided in SI section 2 and discussed in the context of consumer experience improvements in section 5.2, we then calculate the overall LED efficiency in 2003 and 2010, shown in Figure 5 as a waterfall diagram across all sub-efficiencies, and in 2016 and 2020, similarly shown in Figure 6. The overall white LED lamp efficiency improved from $\eta_L=5.8\%$ in 2003 to $12.6\%$ in 2010, $32.5\%$ in 2016 and finally to $38.7\%$ in 2020. As shown in the panels of Figure \ref{fgr:waterfall}, no single loss channel dominates in terms of its contribution to the overall efficiency, in line with previous observations\cite{tsao2010solid}. We note, however, that the loss channels with a fixed physical limit, e.g., Stokes loss that contributes to the conversion efficiency by phosphors, became more dominant in 2016 and 2020 compared to 2003 and 2010.

Figure \ref{fgr:breakthroughs_efficiency} shows the overall magnitude of contributions of identified LED innovations and technology spillovers to improvements in LED efficiency over time across different sub-efficiencies. The list of technology spillovers identified in our study is provided in Table \ref{tab:spillovers} and discussed in Section \ref{subsec:spillovers}. Through the index decomposition analysis described in Section \ref{subsec:metrics}, we find that in the overall LED efficiency increase of 32.9\% from 5.8\% to 38.7\% between 2003 and 2020, at least 2.8\% of which can be attributed specifically to technology spillovers identified in this study, corresponding to 8.5\% of the total LED efficiency improvements between 2003 and 2020.

In Figure \ref{fgr:breakthroughs_efficiency} we also compare, for the first time, efficiency improvements across sub-efficiencies over time, contrasting them with the physical limits of corresponding loss channels. We find that there has been consistent progress across all device sub-efficiencies in the recorded period. Specifically, between 2003 and 2020, forward voltage efficiency increased from 70\% to 99.5\%, internal quantum efficiency from 55\% to 90\%, electrical droop from 65\% to 90\%, light extraction efficiency from 60\% to 90\%, spectral efficiency from 74\% to 83\%, conversion efficiency (red) from 11\% to 45\%, conversion efficiency (green) from 19\% to 61\%. Notably, some sub-efficiencies for the most recent devices considered in our study are now within $\sim10\%$ of their respective physical limits. The exception is spectral efficiency, which at $\sim17\%$ below the physical limit shows larger potential for further improvements.
